\begin{acknowledgments}

I would like to thank my advisor, Tom Humanic, for all of his support these many years, and Mike Lisa as well.
I appreciate them for their mentorship and for guiding my research, challenging my assumptions, and sharing decades of experience with me.
I owe many thanks to them and to The Ohio State University physics department for an excellent education and the opportunity to travel the world in the name of science. 
Thanks to Kris Dunlap; she is the glue that holds the department together, and every student owes her a debt for the often unseen service and support she provides.

I am also indebted to the current and former students in the OSU Experimental Nuclear Physics group, and to the theorists across the hall. 
They were there at the start to mentor me as I was trying to wrap my head around this field, and they've been alongside me ever since.
Whether I needed a physicist's intuition, a programming tutor, a math consultant, or just someone to listen as I babbled in front of a white board, they were there.

I want to thank the ALICE Collaboration for allowing me to participate in cutting-edge science.
I'm particularly thankful to the AliFemto research group, within which I have found mentors, colleagues, and friends.

Thanks to Willamette University and University Prep for nurturing my curiosity and appreciation of science.
I would never have ended up here if not for the strong role models I had each step of the way.

I must thank my family and friends for years of love, support, and encouragement.

Finally, I thank my loving wife Amy for everything. Just everything.

% Mike
% osu group (call out John?)
% alice collaboration
% femtoscopy group
% Amy
% family
% friends


\end{acknowledgments}
