\begin{vita}
\dateitem{September 20, 1985}{Born---Seattle, WA}
\dateitem{May 2004}{University Preparatory Academy}
\dateitem{May 2008}{B.A. in Physics and Philosophy, Willamette University, Salem, Oregon}
\dateitem{August 2012}{M.S. in Physics, The Ohio State University, Columbus, Ohio}

% Insert other relevant items here (GTA, etc.)
%
%\begin{publist}
%\pubitem{``Kinetic effects of solid density perturbations produced by intense laser pulses incident on reduced mass targets in {LSP}'' F. W. King, C. Orban, D. W. Schumacher, \textit{In internal review}.}
%\pubitem{``Modeling the effects of front-surface structures on target normal sheath acceleration using handoffs between multiple simulations" M. M. McMahon, F. W. King, D. W. Schumacher, \emph{et al.} \textit{In internal review}.}
%\pubitem{``Order and chaos in the rotation and revolution of a line segment and a point mass'' J. F. Lindner, J. Lynn, F. W. King, A. Logue, \textit{Phys. Rev. E} \textbf{81}, 036208 (2010).}
%\end{publist}

%\input{Publications.tex}

\begin{preslist}
\presitem{``Simulations of High Intensity Short Pulse Lasers Incident on Reduced Mass Targets Using LSP'' F. W. King, C. Orban, K. U. Akli, D. W. Schumacher, E. A. Chowdhury, C. D. Andereck, D. W. Schumacher, \textit{Ohio Supercomputer Center Statewide User Group Meeting}, Columbus, OH (2015).}
\presitem{``Simulations of high intensity short pulse lasers incident on reduced mass targets using LSP" F. W. King, C. Orban, K. U. Akli, D. W. Schumacher, \textit{2014 meeting of the APS Division of Plasma Physics}, New Orleans, LA (2014).}
\presitem{``LSP simulation of the evolution of reduced mass targets" F. W. King, D. W. Schumacher, K. U. Akli, R. R. Freeman, \textit{Frontiers in Extreme Relativistic Optics}, Columbus, OH, (2013).}
\presitem{``LSP simulations of high intensity short pulse lasers incident on reduced mass targets" D. W. Schumacher, F. W. King, \textit{21st Annual Meeting Fusion Science Center for Extreme States of Matter}, Key West, FL (2012).}
\presitem{``LSP simulations of high intensity short pulse lasers incident on reduced mass targets" F. W. King, C. Orban, K. U. Akli, D. W. Schumacher, \textit{2011 meeting of the APS Division of Plasma Physics}, Salt Lake City, UT (2011).}
\presitem{``Heating of reduced mass targets" F. W. King, V. M. Ovchinnikov, D. W. Schumacher, K. U. Akli, R. R. Freeman, \textit{Fusion Science Center Meeting, Columbus}, OH (2011).}
\presitem{``Two-photon interference with two (and only two) independent photons" F. W. King, M. Trias, M. Ligare, \textit{2009 Meeting of the APS Division of Atomic, Molecular, and Optical Physics}, Charlottesville, VA, (2009).}
\presitem{``Simulating a charged spherical pendulum in time-varying electric and magnetic fields" M. Wellons,  F. W. King, T. McAlpine, \textit{2008 March Meeting of the APS}, New Orleans, LA, (2008).}
\end{preslist}

\begin{fieldsstudy}
\majorfield{Physics}
%\onestudy{High Energy Density Physics}{Prof. R.R. Freeman {\&} Prof. L. Van Woerkom} % optional
% Alternatively you can do:
%\begin{studieslist}
% \studyitem{High Energy Density Physics}{Prof. R.R. Freeman {\&} Prof. L. Van Woerkom}
% \studyitem{Laser design and operation}{Dr. E.A. Chowdhury}
% \studyitem{Topic 3}{Professor 3}
%\end{studieslist}
\end{fieldsstudy}

\end{vita}
